### 2016-01-12 _site/countModel/countData.Rmd
github pages update???

---
title: "negativeBinomial"
author: "John Tipton"
date: "August 14, 2015"
output: html_document
---

@@

```{r, echo=FALSE}
library(parallel)
estimate_params <- function(model, data, pars = pars, iter=5000){
  sflist <- mclapply(1:4, mc.cores = 4,
             function(i) stan(fit = model, data = data, pars = pars,
                              chains = 1, chain_id = i,
                              iter=iter,
                              refresh = -1))
  fit <- sflist2stanfit(sflist)
  return(fit)
}
# m <- sampling(sm, data = list(N = length(count), y = count, X = X, p=dim(X)[2]),
#   pars = c("beta", "phi"),
#   iter = 5000, chains = 4)
m <- estimate_params(sm, data = list(N = length(count), y = count, X = X, p=dim(X)[2]),  pars = c("beta", "phi"))
```

>>>>

@@

```{r, echo=FALSE}
library(parallel)
estimate_params <- function(model, data, pars = pars, iter=5000){
  sflist <- mclapply(1:4, mc.cores = 4,
             function(i) stan(fit = model, data = data, pars = pars,
                              chains = 1, chain_id = i,
                              iter=iter,
                              refresh = -1))
  fit <- sflist2stanfit(sflist)
  return(fit)
}
# m <- sampling(sm, data = list(N = length(count), y = count, X = X, p=dim(X)[2]),
#   pars = c("beta", "phi"),
#   iter = 5000, chains = 4)
m <- estimate_params(sm, data=list(N=length(count), y=count, X=X, p=dim(X)[2]),
                     pars=c("beta", "phi"))
```
